Counting infinitely by Oritatami co-transcriptional folding

### 2019-06-27 paper.tex
intro cont...

A shape of RNA depends on the DNA sequence.
Geary, Rothemund, and Andrsen have succeeded in experimentally making 2D RNA tiles (Fig.\ref{fig:rna_origami}) by repeatedly copying a specific DNA sequence \cite{GearyRothemundAndersen2014}.
Then, Oritatami System was designed as a mathematical model that the process of RNA production and Fig.\ref{fig:origami_on_oritatami} is the 2D RNA tile which is represented on Oritatami System.

>>>>

A shape of RNA depends on the DNA sequence.
Geary, Rothemund, and Andrsen have succeeded in experimentally making 2D RNA tiles (Fig.\ref{fig:rna_origami}) by repeatedly copying a specific DNA sequence \cite{GearyRothemundAndersen2014}.
Then, Oritatami System was designed as a mathematical model that the process of RNA production \cite{counter2016} and Fig.\ref{fig:origami_on_oritatami} is the 2D RNA tile which is represented on Oritatami System.
Oritatami system treats transcript and nucleobase as paths and vertices which called \textit{bead}, respectively, moreover, they are arranged on a triangular grid.
The system takes transcript as an input and output an terminal conformation.
Geary et al. implemented binary counter in this system \cite{counter2016}.
This counter is folded in zigzags, and each row represents a counted number.
Then, this counter is given a bit width as an input to the system before transfer begins, and encounters nondeterminism if it carries beyond that bit width.
Since it is running on deterministic system, it halts when it becomes nondeterministic.

In this paper, based on the implementation method of this counter, we implement a counter which defined the behavior that extends the bit width when it overflows.
